State of the Practice for Lattice Boltzmann Method Software

### 2022-01-26 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Revisions to section 3.2 Surface Correctness and Verifiability

\subsection{Surface Correctness and Verifiability}

Seventeen of the software packages include a requirements specification artifact
or explicitly reference domain theory, often only the latter. Software packages
that distribute requirements specification information, such as DL\_MESO (LBE),
generally keep it brief and include it within other documentation. This artifact
is often found within a user manual, on a web-page, or is mentioned in related
publications. In the latter case the user may need to spend significant time to
find this information.  \wss{More on requirements as a pain point is given in
Weiss, and other papers cited by Carver (2021).  Isn't generally requirements in
the SE sense of following a template or similar.}

@@

The use of continuous integration tools and techniques alludes to a more refined
development process where faults are isolated and better recognized. Only three
of the packages (ESPResSo, Ludwig, Musubi) mentioned applying the practice of
continuous integration in their development process. \wss{Forward reference that
suggests more tools use CI (Section 7 Comparison of Principles, Process and
Methodologies to Research Software in General).}

@@

Figure~\ref{Fig_CorrectnessVerifiability} shows the surface correctness and
verifiability ranking of the software packages using AHP. Software packages with
a higher score tend to have a visible requirements specification or references
to theory documentation. They also explicitly use at least one document
generation tool that builds confidence of correctness. The top ranked software
packages all include an easy to follow getting started tutorial, and most of
these include expected output. The two top ranked packages, Ludwig and Musubi, indicate the use of unit testing in their documentation. They also incorporated continuous integration in the development process. Furthermore, eight of the top 10 ranked packages are noted as being alive.

The inclusion of requirements specification and theory documentation greatly
benefits the correctness and verifiability of software packages. The use of
document generation tools can help build confidence in correctness. The addition
of easy to follow tutorials further helps users verify the software and have
confidence in its correctness. Unit testing, as well as the use of continuous
integration tools and techniques such as Bamboo, Jenkins, and Travis CI, help
verify correctness.

@@

@@

>>>>

\subsection{Surface Correctness and Verifiability} \label{SecSurfCorrectAndVerifiab}

Seventeen of the software packages explicitly reference domain theory, but a
full requirements specification, in the software engineering sense
\citep{IEEE1998, RobertsonAndRobertson1999Vol, ESA1991}, is absent from all of
the projects. Software packages that include a subset of a requirements
specification, such as DL\_MESO (LBE), keep the information brief and include it
within other documents. When present, theory related information is generally
found within a user manual, on a web-page, or in a cited publication. In the
latter case significant time may be needed to track down the information.

@@

The use of continuous integration tools and techniques alludes to a more refined
development process where faults are isolated and better recognized. Only three
of the packages (ESPResSo, Ludwig, Musubi) mentioned applying the practice of
continuous integration in their development process.

@@

Figure~\ref{Fig_CorrectnessVerifiability} shows the ranking for surface
correctness and verifiability. Software packages with a higher score tend to
have theory documentation. They also explicitly use at least one document
generation tool that helps with verification, thus building confidence in
correctness. The top ranked software packages all include an easy to follow
getting started tutorial, and most of these include expected output. The two top
ranked packages, Ludwig and Musubi, indicate the use of unit testing in their
documentation. They also incorporated continuous integration in the development
process. Furthermore, eight of the top 10 ranked packages are noted as being
alive.

@@

\wss{Document theory (17 of the packages), but not requirements.  Might think
 this is good enough, but a theory manual doesn't include the traceability to
 the code.  For instance, what are the consequences of changing an assumption?}

 \wss{More on requirements as a pain point is given in Weiss, and other papers
cited by Carver (2021).  Isn't generally requirements in the SE sense of
following a template or similar.}

@@

Section \ref{SecSurfCorrectAndVerifiab} shows that continuous integration is
rare in LBM.
